### 2015-09-10 fundamentals/fcsreqs.tex

A final benefit of the discreteness of facilities and materials is their power
when combined. The ability to track a material's history as it moves from one
facility to another is unique to \Cyclus. While some current simulators track
materials in chunks, they do not necessarily preserve chunk identity as the
materials move around the fuel cycle. When coupled with \Cyclus' individual
facility modeling, this capacity becomes distinct from what other fuel cycle
simulators are able to do. So, while FAMILY21 and \gls{COSI} can identify
whether a batch being discharged from a reactor originated in \gls{MOX}
fabrication rather than fresh \gls{UOX} fabrication, \Cyclus can go further,
tracking which of the fresh batches contained material from a particular
discharged batch. By extension, \Cyclus can also report which individual
facilities the batch passed through and in which it originated. The
nonproliferation-related applications of this analysis capability are
significant - allowing \Cyclus to answer questions that previous simulators
have been unable to ask.

>>>>

A final benefit of the discreteness of facilities and materials is their power
when combined. The ability to track a material's history as it moves from one
facility to another is unique to \Cyclus. While some current simulators track
materials in discrete quanta, they do not necessarily preserve the identity of each quantum as the
materials move around the fuel cycle. When coupled with \Cyclus' individual
facility modeling, this capacity becomes distinct from what other fuel cycle
simulators are able to do. So, while FAMILY21 and \gls{COSI} can identify
whether a batch being discharged from a reactor originated in \gls{MOX}
fabrication rather than fresh \gls{UOX} fabrication, \Cyclus can go further,
tracking which of the fresh batches contained material from a particular
discharged batch. By extension, \Cyclus can also report which individual
facilities the batch passed through and in which it originated. The
nonproliferation-related applications of this analysis capability are
significant - allowing \Cyclus to answer questions that previous simulators
have been unable to ask.

### 2015-09-10 fundamentals/impl.tex

Automated version control, provided by the well-established \emph{distributed
  version control} tool git \cite{software_freedom_conservancy_git_2014}, is
at the heart of the QA strategy because it records the full history of any
change, along with metadata such as the author, a timestamp, and an
accompanying message. This makes it possible to identify when changes were
introduced, how they related to other changes, and who made those changes.  If
necessary, it also facilitates reversing individual changes from a long and
intricate set of changes.  Version control also enables a code review process
descried in section \ref{sec:qa-review} below.

@@

\emph{Continuous integration (CI)} is the idea that software should be tested
and validated as it is being developed, rather than as a final stage in a
longer development cycle.  Under \gls{CI}, every pull request is automatically
tested independently immediately as it is proposed. The results of this
testing are shown to code reviewers in the GitHub interface.  The \Cyclus
project currently uses the CircleCI service for continuous integration.
Whenever a pull request is created, CircleCI builds a version of the \Cyclus
source code that includes the requested changes and runs the complete test
suite, reporting back whether or not those steps were successful. If \gls{CI}
was not successful, the code author(s) must first identify and resolve the
problems.

>>>>

Automated version control, provided by the well-established \emph{distributed
  version control} tool git \cite{software_freedom_conservancy_git_2014}, is
at the heart of the QA strategy because it records the full history of any
change, along with metadata such as the author, a timestamp, and an
accompanying message. This makes it possible to identify when changes were
introduced, how they are related to other changes, and who made those changes.  If
necessary, it also facilitates reversing individual changes from a long and
intricate set of changes.  Version control also enables a code review process
descried in section \ref{sec:qa-review} below.

@@

\Gls{CI} is the idea that software should be tested
and validated as it is being developed, rather than as a final stage in a
longer development cycle.  Under \gls{CI}, every pull request is automatically
tested independently, immediately as it is proposed. The results of this
testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
project currently uses the CircleCI \cite{circleci} service for continuous integration.
Whenever a pull request is created, CircleCI builds a version of the \Cyclus
source code that includes the requested changes and runs the complete test
suite, reporting back whether or not those steps were successful. If \gls{CI}
was not successful, the code author(s) must first identify and resolve the
problems.
